Supporting Information

### 2018-02-27 SupportingInformation.Rmd
small further changes

### Model selection approach
```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v,mtime(list("OurBiCopSelect.R")))}
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```
The test of indepedence gave $p=$ `r BivMS_res_Loecke$IndepTestRes`.

@@

### Non-paramtric analysis of tail dependence
<!--Do the analysis-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v,mlist(list("CopulaFunctions.R","copsurrog2d.R","NonParamStat.R")))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

>>>>

### Model selection approach
```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v,mtime("OurBiCopSelect.R"))}
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v[,1],u2=v[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```
The test of indepedence gave $p=$ `r BivMS_res_Loecke$IndepTestRes`.

@@

### Non-paramtric analysis of tail dependence
<!--Do the analysis-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v,mtime("CopulaFunctions.R"),mtime("copsurrog2d.R"),mtime("NonParamStat.R"))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"
